Spectroscopic confirmation of very-wide stellar binaries and large-separation comoving pairs from \textsl{Gaia DR1}

### 2017-07-29 paper/comoving-followup.tex
another ref

Going forward, definitive confirmation of comoving star pairs may require
precise measurements of chemical abundances combined with precise radial
velocities, as demonstrated with the \acronym{LAMOST} data.
However, we would also like to \emph{test} assumptions about chemical
homogeneity, rather than simply assuming that all true comoving pairs must have
identical abundances.
For example, the outcomes of planet formation may lead to large or appreciable
abundance differences between coeval stars (e.g., \citealt{yo}, Oh et al.,
submitted).
We therefore caution that---to study the chemical properties of comoving pairs
and star formation in general---the comoving pairs should be selected from their
kinematics alone.

>>>>

Going forward, definitive confirmation of comoving star pairs may require
precise measurements of chemical abundances combined with precise radial
velocities, as demonstrated with the \acronym{LAMOST} data.
However, we would also like to \emph{test} assumptions about chemical
homogeneity, rather than simply assuming that all true comoving pairs must have
identical abundances.
For example, the outcomes of planet formation may lead to large or appreciable
abundance differences between coeval stars (e.g., \citealt{Pinsonneault:2001},
Oh et al., submitted).
We therefore caution that---to study the chemical properties of comoving pairs
and star formation in general---the comoving pairs should be selected from their
kinematics alone.
